---
title       : Developing Data Products Presentation
subtitle    : Histogram of Random Data
author      : ABrunk
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Application Overview

Sometimes, it is helpful to be able to generate a visual representation of a normal distribution using a set of chosen inputs.  This application allows the user to provide a set of inputs and then generates a chart illustrating how a set of normally distributed data would appear using that information.

--- .class #id 

## Application Inputs

The application takes in three inputs:

1. The number of data points
2. The mean value of the points in the distribution
3. The standard deviation of the points in the distribution

The N must be between 1 and 1000, while the mean and standard deviation must be between 0 and 1000.

```{r eval=FALSE}
        numericInput('id_n','Number of Data Points',
                     1,min=1,max=1000,step=1),
        numericInput('id_mean','Mean Value',
                     0,min=0,max=1000,step=1),
        numericInput('id_sd','Standard Deviation',
                     0,min=0,max=1000,step=1)
```

--- .class #id 

## Application Calculations

Once the data is entered, a set of normally distributed data is generated using the `rnorm` function as follows:

```{r eval=FALSE}
my_data <- reactive(rnorm(n=input$id_n,mean=input$id_mean,sd=input$id_sd))
```

For example, if we use `n = 20`, with a mean of `10` and a standard deviation of `2` then the data generated is as follows:

```{r echo=FALSE}
my_data <- rnorm(n=20,mean=10,sd=2)
print(my_data)
```

--- .class #id 

## Application Output

Finally, the app outputs a histogram of the data using the following server code:
```{r eval=FALSE}
hist(my_data(),xlab='Numeric Value',ylab='Count of Data Points',col='red',main='Histogram')
```

```{r echo=FALSE}
hist(my_data,xlab='Numeric Value',
                    ylab='Count of Data Points',
                    col='red',
                    main='Histogram')
```

